---
title: "Group 33 CA Pollution Burden"
author: "Kristin Gill and Quinlan Smith"
date: "11/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```

```{r}
# read in the data
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

``````{r, message = FALSE, warning = FALSE}
ces %>% 
  ggplot(aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() +
  labs(x = "Percentage of Population White",
       y = "CalEnvrioScreen 3.0 Score",
       title = "CalEnviroScreen 3.0 Scores vs. Percentage of Population White") +
  scale_fill_gradient(low = "navy", high = "orange") +
  theme_minimal()
```

This visualization shows a negative correlation between CalEnvironScreen 3.0 scores and the percentage of the census tract population that identifies as white; as the percentage white increases, the CES 3.0 score decreases. A higher score indicates higher pollution burden and vulnerability, so census tracts with a higher percentage of whites tend to have lower pollution burdens. 
